---
title: "Maura Anish Final Dashboard"
bibliography: dashboardReferences.bib
output: 
  flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
```

## Introduction {.sidebar}
This dashboard was constructed for DACSS 690V: Data Visualization, a course taught by Dr. Jose Manuel Magallanes Reyes in the Winter 2025 session at the University of Massachusetts Amherst. As of January 24, 2025, this dashboard contains three plots: 1) a boxplot of student-teacher ratios at K-12 schools in Washington, which refers to @heckmann_ratio_2024 for additional context, 2) a side-by-side boxplot of crimes committed in Massachusetts, according to the age of the perpetrator, and 3) a map of Boston with information about political donations made in 2024.

### References
<div id="refs"></div>

## Column {.tabset .tabset-fade}

### Univariate Plot
```{r}
readRDS("uniplot.rds")
```

### Bivariate Plot
```{r}
readRDS("biplot.rds")
```

### Choropleth Map
```{r}
readRDS("bostonmap.rds")
```